---
title: "Read data for penAFT model"
author: "Anonymous"
date: "August 1st, 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Read data for penAFT model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r knitr-setup, include = FALSE, comment="#>", eval=FALSE}
knitr::opts_chunk$set(
  collapse  = TRUE,
  results   = "markup",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)
```

# R session setup

```{r Rsetup-ls, echo=FALSE}
rm (list=ls())
```

```{r Rsetup}
sessionInfo()
```

```{r input-info, echo=FALSE}
xlsxnm <- "datain/jnpx_scrambled_053122.xlsx"
xlsxbs <- basename(xlsxnm)
vignette_nm  <- "11-data"
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
```


* This is `r vignette_nm` vignette that illustrates how to process  `r xlsxbs` data.
* Rmd file  `r vignette_Rmd` was executed at `r Sys.time()`
* Script requires that `r xlsxbs` is stored in `datain` subfolder.



# Create dtc dataset

Data frame `dtc` with complete cases created from `r xlsxbs` dataset.


##  Preprocessing raw data

* Original raw data are stored in .xlsx format
* Vector `nms_raw` contains original variable names
* Variable `CASE_CONTROL` renamed to `status`
* For consistency variable names were converted to lower case

```{r dat-raw}

xlsx  <- readxl::read_excel(xlsxnm, sheet = "joslin_npx_scrambled", na = "", guess_max = 1000)
dat_raw <- data.frame(xlsx)

nms_raw <- names(dat_raw)
nms_raw[nms_raw == "CASE_CONTROL"] <- "status"   # status = 1 (observed follow-up time), status = 0 (censored follow-up time)

nms_low <- tolower(nms_raw)
(names(dat_raw) <- nms_low)
```

Auxiliary lists of variable names in `dat_raw` are created.

* `prt_vnms`: names of protein variables
* `cln_vnms`: names of clinical variables


```{r var-names-lists}
(prt_vnms <- nms_low[which(nms_low == "kim1.npx") : length(nms_low)])
length(prt_vnms)
cln_vnms  <- c("sex",    "sbp_tl",       "dbp_tl", "ageonset_tl", "bmi_tl",
              "age_tl", "b_hba1c_prc",  "du_acr", "bl_egfr")
```

* `dat_anl`: analytical dataset with a subset of variables.

```{r dat-anl}
select_vars <-  c("fu_time", "status", cln_vnms, prt_vnms)
dat_anl <- dat_raw[,select_vars]
class(dat_anl)
dim(dat_anl)
names(dat_anl)
```

Summarize  number of missing values in analytical dataset. This step may be helpful to identify variables
with a large number of missing values and decide whether to keep it or not.   

```{r missing-values}
count_miss_vals <- sapply(dat_anl, function(x) sum(is.na(x)))
count_miss_vals <- sort(count_miss_vals, decreasing = TRUE) 
ncol(dat_anl)                          # Number of variables in analysis
sum(count_miss_vals == 0)              # Number of variables without missing values  
count_miss_vals[count_miss_vals  >  0] # Variables with missing values
```

Remove variables with excessive number of missing values

```{r remove-vars-miss-vals}
dat_anl[, c("bmi_tl")] <- NULL
(cln_vnms2 <- cln_vnms[! cln_vnms %in% c("bmi_tl")]) 
X_vnms <- c(cln_vnms2, prt_vnms)
```

``` 
Select subset of rows with *complete*  cases

```{r dtc-cmplt-cases}

cmplt_cases <- complete.cases(dat_anl)
dtc <- dat_raw[cmplt_cases, ]  # Data with complete cases
nrow(dtc) # Number of rows with complete data
```

```{r save-dtc}}
fnm <- "Rdata/11-dtc.Rdata"
save(dtc, file = fnm )
```

Data frame `dtc` with complete cases contains `r nrow(dtc)` rows  and `r ncol(dtc)` columns. 

## Create X, Y and Xnew matrices


Extract `X` and `Y` from `dtc` data frame with complete cases.

```{r XYmtx}
X    <- as.matrix(dtc[, X_vnms]) 
logY  <- log(dtc[, "fu_time"]) 
delta <- dtc[, "status"]      # status = 0 indicates censored observation 
n <- length(logY)
```

* Xnew matrix extracted from X for illustration. Rows with _uncensored_ `time_fu` selected.


```{r XY-new}
sel_rows <- delta == 1
Xnew <- X[sel_rows,]
logYnew <- logY[sel_rows] 
```

Save matrices for model fitting.

```{r save-mtx}}
fnm <- "Rdata/11-mtx.Rdata"
save(X,logY, delta, file = fnm )

fnm <- "Rdata/11-mtxnew.Rdata"
save(Xnew, logYnew, file = fnm )
```



