---
title: "penAFT.cva"
author: "Anonymous"
date: "September 7th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


# R session setup

```{r vignette-nm, include=FALSE}
.vignette_nm = "12-cva"
```

```{r Rmd-global-info, include = FALSE, file = "05-global-info.R"}
## The code executed in R script, will not appear in rendered .html file
```

```{r Rsetup}
sessionInfo()
```


* This is `r .vignette_nm` vignette that illustrates how to create `cva` object
* Rmd file  `r .vignette_Rmd` was executed at `r Sys.time()`
* Note: It takes several minutes to execute this script


```{r load-Rdata}
library(penAFT)
sessionInfo()
load(file = "raw-Rdata/11-mtx.Rdata")
ls()
```

## penAFT.cva 


# Notes: alpha is a numeric vector with values ranging from 0 to 1 
# Setting seed to  constant allows to use the same folds for all elements of alpha
# lambda is null

```{r penAFT-cva, cache=TRUE}
library(cvaUtils)

alpha <- seq(0, 1, len = 11)^3
lmbda <- 10^(seq(3,-5, -0.2))
penAFTcva.en <- penAFT.cva(x=X, logY = logY, delta = delta,
               alpha = alpha,
               nlambda = 50, lambda.ratio.min = 0.1, lambda = lmbda,
               penalty = "EN", nfolds = 5, seed = 123)
class(penAFTcva.en) # "penAFT.cva"
str(penAFTcva.en)
```


Save cva object

```{r save-penAFT-cva}
save(penAFTcva.en,file = "Rdata/12-cva.Rdata")
```
* Rmd file  `r .vignette_Rmd` completed execution at `r Sys.time()`

