---
title: "penAFT: Optimal hyperparameters"
author: "Anonymous"
date: "August 7th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---

# R session setup

```{r vignett-nm, include=FALSE}
.vignette_nm = "13-opt"
```

```{r Rmd-global-info, include = FALSE, file = "05-global-info.R"}
## The code executed in R script, will not appear in rendered .html file
```

# Setting the stage

## R session setup

```{r Rsetup}
library(cvaUtils)
sessionInfo()
```


* This is `r .vignette_nm` vignette that illustrates how to find optimal values of hyperpramaters for `cva` object
* Rmd file  `r .vignette_Rmd` was executed at `r Sys.time()`
* cva object `penAFTcva.en` is loaded from an external file

## Load objects
```{r load-Rdata}
load(file = "Rdata/12-cva.Rdata")
ls()
```

# Optimal values of hyperparameters

Goal: Find optimal values of alpha and lambda hyperparameters using C-V.

## Loss grid for cva object

* Create data frame with for a grid of hyperparameter values  

```{r cva-lossgrid}
loss_grid <- lossgrid(penAFTcva.en)
names(loss_grid)
save(loss_grid, file = "Rdata/13-loss-grid.Rdata")
```

## minmissplot

* Auxiliary plot for all values of alpha and lambda

```{r minlossplot-all}
minlossplot(penAFTcva.en, plot.it ="all")
```

* Default plot with minimum loss for each alpha

```{r minlossplot-min}
minlossplot(penAFTcva.en)
```

## Explore loss_grid data frame

```{r cva-lossgrid-optm}
# loss_grid_lambda_min <- loss_grid[, "lambda.min"] 
# loss_grid[loss_grid_lambda_min, ]
loss_grid_cv.err.linPred_min <-loss_grid[,"cv.err.linPred_min"]
loss_grid[loss_grid_cv.err.linPred_min, ]
```

* Extract optimum values

```{r extract-opt}
alpha   <- unique(loss_grid$alpha)
(alpha0 <-alpha[11])

dta0 <- subset(loss_grid, alpha == alpha0) # select rows for alpha0
dt1 <-  subset(dta0, cv.err.linPred == min(cv.err.linPred))
(lambda0 <- dt1[["lambda"]])

```

