---
title: "penAFT: Optimal Model fit"
author: "Anonymous"
date: "September 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---

# R session setup

```{r vignette-nm, include=FALSE}
.vignette_nm = "14-fit"
```

```{r Rmd-global-info, include = FALSE, file = "05-global-info.R"}
## The code executed in R script, will not appear in rendered .html file
```

```{r Rsetup}
library(cvaUtils)
library(penAFT)

sessionInfo()
```

* This is `r .vignette_nm` vignette that illustrates how to fit model using optimal values of hyperpramaters for `cva` object
* Rmd file  `r .vignette_Rmd` was executed at `r Sys.time()`

# Optimal values of hyperparameters

Goal: Find optimal values of alpha and lambda hyperparameters using C-V.

## Loss grid for cva object

* Loss values on a grid of parameter values is loaded from an external file

```{r load-Rdata}
load(file = "raw-Rdata/11-mtx.Rdata")
load(file = "Rdata/13-loss-grid.Rdata")
ls()
```

* Extract optimum values

Extract optimum values alpha0 and lambda0 (use code from 13-opt.Rmd)

```{r extract-opt}
alpha   <- unique(loss_grid$alpha)
(alpha0 <-alpha[11])

dta0 <- subset(loss_grid, alpha == alpha0) # select rows for alpha0
dt1 <-  subset(dta0, cv.err.linPred == min(cv.err.linPred))
(lambda0 <- dt1[["lambda"]])
```

## Find solution path for a given alpha

Find regularized semiparametric AFT model (alpha = `r alpha0`).

```{r fit-en, cache = TRUE}
fit.en <- penAFT(X = X, logY = logY, delta = delta,
                   lambda  = lambda0,
                   penalty = "EN",
                   alpha = alpha0)
```

Save fit.en object

```{r save-fit-en}
save(fit.en, file ="Rdata/14-fit.Rdata")
str(fit.en)
```




