---
title: "penAFT: Optimal hyperparameters"
author: "Anonymous"
date: "August 7th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


```{r Rmd-init, include = FALSE}
## The code in this chunk will be executed, will not appear in rendered .html file

##  Silently sets knitr chunk options used in Rmd file
require(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  comment="#>",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)

# Silently clears Global environment
rm(list=ls())

# Create .params list  # <- !!! 
.params <- list(vignette_nm = "14-fit"
                ) 

# Silently assign variables for later use
vignette_nm  <- .params$vignette_nm   # .params refers to list defined above
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
vignette_R   <- paste(vignette_nm,".R",   sep = "")
vignette_html<- paste(vignette_nm, ".html",   sep = "")
```

# R session setup


```{r Rsetup}
library(cvaUtils)
sessionInfo()
```

* This is `r vignette_nm` vignette that illustrates how to fit model using optimal values of hyperpramaters for `cva` object
* Rmd file  `r vignette_Rmd` was executed at `r Sys.time()`

# Optimal values of hyperparameters

Goal: Find optimal values of alpha and lambda hyperparameters using C-V.

## Loss grid for cva object

* Loss values on a grid of parameter values is loaded from an external file

```{r load-Rdata}
load(file = "raw-Rdata/11-mtx.Rdata")
load(file = "Rdata/13-loss-grid.Rdata")
ls()
```

* Extract optimum values

Extract optimum values alpha0 and lambda0 (see 13-opt.Rmd)

```{r extract-opt}
alpha   <- unique(loss_grid$alpha)
(alpha0 <-alpha[11])

dta0 <- subset(loss_grid, alpha == alpha0) # select rows for alpha0
dt1 <-  subset(dta0, cv.err.linPred == min(cv.err.linPred))
(lambda0 <- dt1[["lambda"]])
```

## Find solution path for a given alpha

Find solution path for the regularized semiparametric AFT model (alpha = `r alpha0`).

```{r fit-en, cache = TRUE}
fit.en <- penAFT(X = X, logY = logY, delta = delta,
                   nlambda = 50, lambda.ratio.min = 0.01,
                   penalty = "EN",
                   alpha = alpha0)
```
save fit_en object

```{r save-fit-en}
save(fit.en, file ="Rdata/14-fit.Rdata")
str(fit.en)
```


