---
title: "penAFT: Summary of the Optimal Model Fit"
author: "Anonymous"
date: "August 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


```{r Rmd-init, include = FALSE}
## The code in this chunk will be executed, will not appear in rendered .html file

##  Silently sets knitr chunk options used in Rmd file
require(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  comment="#>",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)

# Silently clears Global environment
rm(list=ls())

# Create .params list  # <- !!! 
.params <- list(vignette_nm = "15-fit-summ"
                ) 

# Silently assign variables for later use
vignette_nm  <- .params$vignette_nm   # .params refers to list defined above
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
vignette_R   <- paste(vignette_nm,".R",   sep = "")
vignette_html<- paste(vignette_nm, ".html",   sep = "")
```

# R session setup


```{r Rsetup}
library(penAFT)
sessionInfo()
```

* This is `r vignette_nm` vignette that illustrates how to extract information from an optimal model fit model
* Rmd file `r vignette_Rmd` was executed at `r Sys.time()`

# Extract info from an optimal model fit 

* Loss values on a grid of parameter values is loaded from an external file

```{r load-Rdata}
load(file = "Rdata/14-fit.Rdata")
ls()
```



Extract model coefficients for lambda0=`lambda0`.

## Optimal model coefficients

Extract model coefficients for alpha0 =`r fit.en$alpha` and lambda0 =`r fit.en$lambda`.

```{r fit-en-coefs} 
lmbda0 <- fit.en$lambda
coef.fit.en_list <- penAFT.coef(fit.en, lambda = lmbda0)
coef.fit.en <- coef.fit.en_list$beta
coef_nms <- names(fit.en$X.mean)
rownames(coef.fit.en) <- coef_nms
coef.fit.en
```
