---
title: "penAFT: Summary of the Optimal Model Fit"
author: "Anonymous"
date: "August 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


```{r Rmd-init, include = FALSE}
## The code in this chunk will be executed, will not appear in rendered .html file

##  Silently sets knitr chunk options used in Rmd file
require(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  comment="#>",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)

# Silently clears Global environment
rm(list=ls())

# Create .params list  # <- !!! 
.params <- list(.vignette_nm = "15-fit-summ"
                ) 

# Silently assign variables for later use
.vignette_nm  <- .params$.vignette_nm   # .params refers to list defined above
.vignette_Rmd <- paste(.vignette_nm,".Rmd", sep = "")
.vignette_R   <- paste(.vignette_nm,".R",   sep = "")
.vignette_html<- paste(.vignette_nm, ".html",   sep = "")
ls()
```

# R session setup


```{r Rsetup}
library(penAFT)
sessionInfo()
```

# Extract info from an optimal model fit 

* This is `r .vignette_nm` vignette that illustrates how to extract information from an optimal model fit.
* Rmd file `r .vignette_Rmd` was executed at `r Sys.time()`


* Optimal model fit is loaded from an external file

```{r load-Rdata}
load(file = "Rdata/14-fit.Rdata")
ls()
```

* Atributes of `fit.en` object

```{r fit-en-attributes}
class(fit.en)
length(fit.en)
names(fit.en)
```


## Optimal model coefficients

Extract model coefficients for optimal values of alpha0 =`r fit.en$alpha` and lambda0 =`r fit.en$lambda`.
Coefficients stored in ` ` are standardized, i.e divided by X.sd

```{r fit-en-coefs} 
(lmbda0 <- fit.en$lambda)
coef.fit.en_list <- penAFT.coef(fit.en, lambda = lmbda0)
coef.fit.en <- coef.fit.en_list$beta
coef_nms <- names(fit.en$X.mean)
rownames(coef.fit.en) <- coef_nms
coef.fit.en

rm(lmbda0, coef.fit.en_list, coef_nms)
```

## Predicted values 

* Load matrices for prediction.

```{r load-newmtx}
ls() # Before load
load(file ="raw-Rdata/11-mtxnew.Rdata")
ls() 
```

* Linear prediction.

Note: From documentation: "It is important to note that the output of `penAFT.predict` function should
not be treated as an estimate of the log-survival time".

```{r fit_en-predict}
(lmbda0 <- fit.en$lambda)
lin_pred <- penAFT.predict(fit.en, Xnew = Xnew, lambda = lmbda0)
plot(logYnew, lin_pred, main= "Predicted versus observed on log10 scale")
```

* Cross-check

```{r fit_en-pred-xcheck}
Xpred <- (Xnew - rep(1, dim(Xnew)[1]) %*% t(fit.en$X.mean))/(rep(1, 
                dim(Xnew)[1]) %*% t(fit.en$X.sd))
.beta <-  fit.en$X.sd * coef.fit.en            
predChk <- Xpred %*% .beta
range(lin_pred-predChk)
```
