---
title: "penAFT: Summary of the Optimal Model Fit"
author: "Anonymous"
date: "August 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


# R session setup

```{r vignette-nm, include=FALSE}
.vignette_nm = "15-fit-summ"
```

```{r Rmd-global-info, include = FALSE, file = "05-global-info.R"}
## The code executed in R script, will not appear in rendered .html file
```

```{r Rsetup}
library(penAFT)
sessionInfo()
```

# Extract info from an optimal model fit 

* This is `r .vignette_nm` vignette that illustrates how to extract information from an optimal model fit.
* Rmd file `r .vignette_Rmd` was executed at `r Sys.time()`


* Optimal model fit is loaded from an external file

```{r load-Rdata}
load(file = "Rdata/14-fit.Rdata")
ls()
```

* Atributes of `fit.en` object

```{r fit-en-attributes}
class(fit.en)
length(fit.en)
names(fit.en)
```


## Optimal model coefficients

Extract model coefficients for optimal values of alpha0 =`r fit.en$alpha` and lambda0 =`r fit.en$lambda`.
Coefficients stored in `coef.fit.en` are standardized, i.e divided by X.sd

```{r fit-en-coefs} 
(lmbda0 <- fit.en$lambda)
coef.fit.en_list <- penAFT.coef(fit.en, lambda = lmbda0)
coef.fit.en <- coef.fit.en_list$beta
coef_nms <- names(fit.en$X.mean)
rownames(coef.fit.en) <- coef_nms
coef.fit.en

rm(lmbda0, coef.fit.en_list, coef_nms)
```

## Predicted values 

* Load matrices for prediction.

```{r load-newmtx}
ls() # Before load
load(file ="raw-Rdata/11-mtxnew.Rdata")
ls() 
```

* Linear prediction.

Note: From documentation: "It is important to note that the output of `penAFT.predict` function should
not be treated as an estimate of the log-survival time".

```{r fit_en-predict}
(lmbda0 <- fit.en$lambda)
lin_pred <- penAFT.predict(fit.en, Xnew = Xnew, lambda = lmbda0)
plot(logYnew, lin_pred, main= "Predicted versus observed on log10 scale")
```

* Cross-check, i.e. manually obtain predicted values

```{r fit_en-pred-xcheck}
Xpred <- (Xnew - rep(1, dim(Xnew)[1]) %*% t(fit.en$X.mean))/
            (rep(1, dim(Xnew)[1]) %*% t(fit.en$X.sd))
.beta <-  fit.en$X.sd * coef.fit.en            
predChk <- Xpred %*% .beta
round(range(lin_pred-predChk), digits = 5) # zeros?
```
