---
title: "penAFT: Summary of the Optimal Model Fit"
author: "Anonymous"
date: "September 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---

# R session setup

```{r vignett-nm, include=FALSE}
.vignette_nm = "11-data"
```

```{r Rmd-global-info, include = FALSE, file = "05-global-info.R"}
## The code executed in R script, will not appear in rendered .html file
```


```{r Rsetup}
library(penAFT)
sessionInfo()
```

```{r load-dtc}
fnm <- "raw-Rdata/11-dtc.Rdata"
load(file = fnm )
ls()
```



```{r surv-AFT}
library(survival)

aft_weibull  <- survreg(Surv(fu_time, status) ~ b_hba1c_prc + du_acr + bl_egfr +
  kim1.npx + wfdc2.npx + cd27.npx + tnfrsf6b.npx + epha2.npx, dist = "weibull", data = dtc)
aft_weibull
```

```{r pred_weibull}
newdt <- dtc
pred_weibull <- predict(aft_weibull, newdata = newdt)
plot(newdt$fu_time, pred_weibull)
```

The psm function in the R rms package is a kind of front-end for survreg 
in the survival package. psm provides the c-index, or at least Somers' Dxy 
that allows you to compute c from the equation Dxy=2×(c−12). 
It does not provide the Brier score which is used more so for binary Y

# Extract info from an optimal model fit 

* This is `r .vignette_nm` vignette that illustrates how to extract information from an optimal model fit.
* Rmd file `r .vignette_Rmd` was executed at `r Sys.time()`


