---
title: "penAFT: Summary of the Optimal Model Fit"
author: "Anonymous"
date: "September 10th, 2022"
output: 
  html_document:
    toc: true
    number_sections: true
---


```{r Rmd-init, include = FALSE}
## The code in this chunk will be executed, will not appear in rendered .html file

##  Silently sets knitr chunk options used in Rmd file
require(knitr)
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  comment="#>",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)

# Silently clears Global environment
rm(list=ls())

# Create .params list  # <- !!! 
.params <- list(.vignette_nm = "21-fit-AFT"
                ) 

# Silently assign variables for later use
.vignette_nm  <- .params$.vignette_nm   # .params refers to list defined above
.vignette_Rmd <- paste(.vignette_nm,".Rmd", sep = "")
.vignette_R   <- paste(.vignette_nm,".R",   sep = "")
.vignette_html<- paste(.vignette_nm, ".html",   sep = "")
ls()
```

# R session setup


```{r Rsetup}
library(penAFT)
sessionInfo()
```

```{r load-dtc}
fnm <- "raw-Rdata/11-dtc.Rdata"
load(file = fnm )
ls()
```



```{r surv-AFT}
#require(survival)
#pacman::p_load(KMsurv)

#library(KMsurv)
library(survival)
#data("kidtran") 

#n = nrow(kidtran)

#kidtran       <- kidtran[sample(n),] 
#kidtran.train <- kidtran[1:(n * 0.8),]
#kidtran.test  <- kidtran[(n * 0.8):n,]


aftmodel  <- survreg(Surv(fu_time, status) ~ b_hba1c_prc + du_acr + bl_egfr +
  kim1.npx + wfdc2.npx + cd27.npx + tnfrsf6b.npx + epha2.npx, dist = "weibull", data = dtc)
aftmodel

#predicted <- predict(aftmodel, newdata = kidtran.test)
```

The psm function in the R rms package is a kind of front-end for survreg 
in the survival package. psm provides the c-index, or at least Somers' Dxy 
that allows you to compute c from the equation Dxy=2×(c−12). 
It does not provide the Brier score which is used more so for binary Y

# Extract info from an optimal model fit 

* This is `r .vignette_nm` vignette that illustrates how to extract information from an optimal model fit.
* Rmd file `r .vignette_Rmd` was executed at `r Sys.time()`


