---
title: "penAFT.cva"
author: "Anonymous"
date: "August 1st, 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{penAFT.cva}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, knitr-setup, include = FALSE, comment="#>", eval=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)
```

# R session setup

```{r Rsetup-ls, include=FALSE}
rm (list=ls())
```

```{r Rsetup}
sessionInfo()
```

```{r input-info, echo=FALSE}
vignette_nm  <- "42-penAFT-cva"
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
```


* This is `r vignette_nm` vignette that illustrates how to create `cva` object
* Rmd file  `r vignette_Rmd` was executed at `r Sys.time()`
* Note: It takes considerable amount of time to execute this script


```{r load-Rdata}
library(penAFT)
sessionInfo()
load(file = "Rdata/41-penAFT-mtx.Rdata")
ls()
```

## penAFT.cva 


# Notes: alpha is a numeric vector with values ranging from 0 to 1 
# Setting seed to  constant allows to use the same folds for all elements of alpha
# lambda is null

```{r penAFT-cva}
library(cvaUtils)

alpha <- seq(0, 1, len = 11)^3
lmbda <- 10^(seq(3,-5, -0.2))
penAFTcva.en <- penAFT.cva(x=X, logY = logY, delta = delta,
               alpha = alpha,
               nlambda = 50, lambda.ratio.min = 0.1, lambda = lmbda,
               penalty = "EN", nfolds = 5, seed = 123)
class(penAFTcva.en) # "penAFT.cva"
str(penAFTcva.en)
```


Save cva object

```{r save-penAFT-cva}
save(penAFTcva.en,file = "Rdata/42-penAFT-cva.Rdata")
```
* Rmd file  `r vignette_Rmd` completed execution at `r Sys.time()`







