---
title: "penAFT: Optimal hyperparameters"
author: "Anonymous"
date: "August 1st, 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{penAFT: Optimal hyperparameters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  results = "markup",
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)
```

# R session setup

```{r Rsetup-ls, include=FALSE}
rm (list=ls())
```

```{r Rsetup}
library(cvaUtils)
sessionInfo()
```

```{r input-info, include=FALSE}
vignette_nm  <- "44-penAFT-fit"
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
```

* This is `r vignette_nm` vignette that illustrates how to find optimal values of hyperpramaters for `cva` object
* Rmd file  `r vignette_Rmd` was executed at `r Sys.time()`
* cva object `penAFTcva.en` isloaded from external file

```{r load-Rdata}
load(file = "Rdata/43-penAFT-loss-grid.Rdata")
ls()
```

# Optimal values of hyperparameters

Goal: Find optimal values of alpha and lambda hyperparameters using C-V.

## Loss grid for cva object

* Create data frame with for a grid of hyperparameter values  

```{r cva-lossgrid}
names(loss_grid)
save(loss_grid, file = "Rdata/43-penAFT-loss-grid.Rmd")
```

## minmissplot

* Auxiliary plot for all values of alpha and lambda

```{r minlossplot-all}
minlossplot(penAFTcva.en, plot.it ="all")
```

* Default plot with minimum loss for each alpha

```{r minlossplot-min}
minlossplot(penAFTcva.en)
```

## Explore loss_grid data frame

```{r cva-lossgrid-optm}
# loss_grid_lambda_min <- loss_grid[, "lambda.min"] 
# loss_grid[loss_grid_lambda_min, ]
loss_grid_cv.err.linPred_min <-loss_grid[,"cv.err.linPred_min"]
loss_grid[loss_grid_cv.err.linPred_min, ]
```

* Extract optimum values

```{r extract-opt}
alpha   <- unique(loss_grid$alpha)
(alpha0 <-alpha[11])

dta0 <- subset(loss_grid, alpha == alpha0) # select rows for alpha0
dt1 <-  subset(dta0, cv.err.linPred == min(cv.err.linPred))
(lambda0 <- dt1[["lambda"]])

```

