---
title: "Test code chunk options"
author: "Anonymous"
date: "August 1st, 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test code chunk options}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-setup, include = FALSE, comment="#>", eval=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  results = "markup",  
  highlight = TRUE,
  fig.width = 12, fig.height=8, fig.path='Figs/'
)
```


# Testing code chunk options

## Test chunk options defined by knitr 

```{r test-knitr-setup}
(test_knitr_setup <- "test-knitr-setup")
```


## Option: include = FALSE

* Option: include = FALSE prevents code and results from appearing in the finished (e.g html) file. 
* R Markdown still runs the code in the chunk, and the results can be used by other chunks
* R statements are _saved_ in tangle file and are ready for execution
* Equivalent to combination of two options: echo=FALSE, results="hide"

```{r input-info, echo=FALSE, results="hide"}
vignette_nm  <- "90-test-chunks"
vignette_Rmd <- paste(vignette_nm,".Rmd", sep = "")
vignette_Rmd
```

```{r test-include, include = FALSE}
(test_include <- "Test include")
```

The following output confirms that code chunk was indeed executed

```{r test-include-check}
exists("test_include")
```


## Commenting out code chunks in tangle file

* echo =FALSE: Corresponding code change does not show in the html file 

```{r test-tangle-out, echo= FALSE, eval=FALSE, comment = "##"}
(test_tangle <- "Test tangle")
```
The following output confirms that code chunk was not executed (as intended)

```{r test-tangleout-check}
exists("test_tangle")
```

## Test figure

```{r test-figure, echo = FALSE, fig.height=4, fig.width=8, dev ="svg"}
plot(cars)
```




